---
title: "flat_check_data.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Check the values of a vector of primary fur colors

You can check if the column of primary fur color contains only allowed values with `check_primary_color_is_ok()`. 

Allowed values are "Gray", "Cinnamon", "Black", and missing values. If the column contains not allowed values, an explicit error message is displayed.

```{r function-check_primary_color_is_ok}
#' Check the values of a vector of primary fur colors
#'
#' @param string Character. A vector with the primary fur color.
#'
#' @return Boolean. TRUE if all colors are correct.
#' @export
#'
#' @examples
check_primary_color_is_ok <- function(string) {
  
  all_colors_OK <- all(
    string %in% c("Gray", "Cinnamon", "Black", NA)
  )
  
  if (isFALSE(all_colors_OK)) {
    stop('The vector of primary fur color contains not allowed colors. Colors should be among values "Gray", "Cinnamon", "Black", or missing values')
  }
  
  return(all_colors_OK)
}
```
  
```{r example-check_primary_color_is_ok}
check_primary_color_is_ok(string = c("Black", "Cinnamon", NA))
check_primary_color_is_ok(string = c("Gray", "Cinnamon", "Gray"))
```
  
```{r tests-check_primary_color_is_ok}
test_that("check_primary_color_is_ok works", {
  
  expect_true(check_primary_color_is_ok(string = c("Black", "Cinnamon", NA))) 
  
  expect_true(check_primary_color_is_ok(string = c("Gray", "Cinnamon", "Gray")))
  
  expect_error(check_primary_color_is_ok(string = c("Gray", "Cinnamon", "Blue")),
               regexp = "The vector of primary fur color contains not allowed colors")
  
})
```

# Check the integrity of the column of primary fur colors
    
You can check the integrity of the primary fur colors of a dataset with `check_squirrel_data_integrity()`. This function checks that the dataset contains a `primary_fur_color` variable, and that this column only contains allowed values ("Gray", "Cinnamon", "Black", and missing values).

```{r function-check_squirrel_data_integrity}
#' Check the integrity of the column of primary fur colors
#'
#' @param df_squirrels Data frame. A dataset with squirrels data.
#'
#' @return Nothing. Use for side effect. Displays a message if everything is ok
#' @export
#'
#' @examples
check_squirrel_data_integrity <- function(df_squirrels){
    
  # Check if there is a primary_fur_color column
  if (isFALSE("primary_fur_color" %in% names(df_squirrels))) {
    stop("There is no primary_fur_color in this dataset")
  }
  
  # Check if the values in the primary_fur_color column are ok
  primary_colors_ok <- check_primary_color_is_ok(df_squirrels$primary_fur_color)
  
  if (isTRUE(primary_colors_ok)){
    message("All primary fur colors are ok")
  }
   
}
```
  
```{r example-check_squirrel_data_integrity}
my_data_squirrels <- readr::read_csv(
  system.file("nyc_squirrels_sample.csv", package = "squirrels")
  )
check_squirrel_data_integrity(my_data_squirrels)
```
  
```{r tests-check_squirrel_data_integrity}
test_that("check_squirrel_data_integrity works", {
  
  # Everything is ok
  my_data_squirrels <- readr::read_csv(system.file("nyc_squirrels_sample.csv", package = "squirrels"))
  
  expect_message(check_squirrel_data_integrity(my_data_squirrels), 
                 regexp = "All primary fur colors are ok") 
  
  # Error : no primary_fur_color column in the dataset
  my_data_squirrels_wrong_colname <- my_data_squirrels %>% 
    dplyr::rename(primary_color = primary_fur_color)

  expect_error(check_squirrel_data_integrity(my_data_squirrels_wrong_colname), 
               regexp = "There is no primary_fur_color in this dataset")
  
  # Error : not allowed colors in the primary_fur_color column
  my_data_squirrels_wrong_colors <- my_data_squirrels %>% 
     dplyr::mutate(primary_fur_color = stringr::str_to_lower(primary_fur_color))
  
  expect_error(check_squirrel_data_integrity(my_data_squirrels_wrong_colors), 
               regexp = "The vector of primary fur color contains not allowed colors")
  
})
```
  

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_check_data.Rmd", 
               vignette_name = "Check data")
```

